%!TEX root = ../RPA_for_Creating_Program_Note.tex

\titlehead{\hfill\small　発行日時 (Publication date)\\~\hfill\customdate}
\subject{\Large--- 関連ドキュメント作成の自動化 ---}
\title{\huge モールドのRDBSの構築とその応用}
\subtitle{\ \\(\thisdocumentversion)}
\date{}
\author{\ \\\small Author: \fontspec{Hui Font}Kurahashi Nobuaki}

\publishers{%
\begin{marker}
\scriptsize\normalfont
本書は一時的に複製されたものです。\\
発行日から6ヶ月以上経過した場合、または新たなバージョンのものが存在する場合は、本書は速やかに破棄してください。
\tcbline*
This document is a temporary copy.
If more than 6 months have passed since the publication date, or if a new version exists, please dispose of this document promptly.
\end{marker}%
}

\uppertitleback{\small
This document was created using \nameTeX{} (\linkLaTeXe, \linkLaTeXthree), specifically utilizing tools such as \linkTeXLive{} 2024, \linkLuaTeX{} (\linkLuaLaTeX, \linkLuaTeXja, \linkLua), \linkKOMAScript{} (\linkScrbook, \linkScrlayerscrpage), \linkBibTeX{} (\linkBibLaTeX{}, \linkBiber), \linkUpmendex, \linkPGFTikZ, and many useful packages, libraries and modules\\
The document was typeset using the {\fontspec{Euler Math}\linkEuler}, \linkAMSFonts, \linkLatinModern, and {\fontspec{HaranoAjiMincho}\linkHaranoAji}{} font families.\\
The \nameTeX{} documents were edited using \linkTeXstudio{} and \linkSumatraPDF.\\
The analytical approximations were computed using \linkWolframAlpha.\\
Numerical calculations were performed using \linkExcel{} functions.\\% and \linkPython.\\
The source codes for the \nameGcode{} programs (\nameArumatikMi) were written using \linkVSCode.\\
Version and issue control for these documents were managed using \linkGit{} (\linkGitHub{} and \linkGitHubDesktop).\\
%The environment for these tools was managed using \linkDocker{} and \linkUbuntu.\\
%The database used was \linkSQLite.\\
\phantom{Q}Thanks to these tools, with the all-around support of \linkChatGPT-4 (\linkMicrosoftCopilot), the creation of the documents and system was made possible.
This was achieved even while I had to navigate solo, finding my way in the quiet corners, despite being a novice with almost all of these tools, softwares and languages.%
}

\lowertitleback{{\scriptsize\relax%
\setcounter{page}{1}%
\begin{spacing}{1.2}%
\setlength{\tabcolsep}{1.8pt}%
\hfill%
\begin{tabular}{rl}
\hologo{TeX}, \linkLaTeX{}, \linkAMSFonts & are trademarks of \linkAMS.\\
\linkWolframAlpha & is a trademark of \linkWolfram.\\
\linkExcel, \linkVSCode{} and \linkMicrosoftCopilot & are trademarks of \linkMicrosoftCorp.\\
\nameArumatikMi{} and \nameKITAMURA & are trademarks of \linkKitamuraMachinery.\\
%\linkPython & is a trademark of \linkPythonSF.\\
\linkGit{} & is a trademark of \linkSFCInc.\\
\linkGitHub{} and \linkGitHubDesktop & are trademarks of \linkGitHubInc.\\
%\linkDocker & is a trademark of \linkDockerInc.\\
%\linkUbuntu & is a trademark of \linkCanonicalLtd.\\
%\linkSQLite & is a trademark of \linkSQLiteConsortium.\\
\linkChatGPT & is a trademark of \linkOpenAI.
\end{tabular}\\
\hrulefill\\
Copyright © 2023, 2024.\\
This document and the system are owned by the individual writer, not any corporation. All rights reserved.
\end{spacing}
\thispagestyle{emptydate}%
}}